Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-09 Ben_Manuscripts/structure_paper/Draft.tex
More figure/caption updates

  \begin{figure}
  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
  	\rowname{parallel displaced}&
  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_25.png}&
  	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]
  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
  	\rowname{sandwiched}&
  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_25.png}&
  	\includegraphics[width=.325\linewidth]{solvated_layered_rzplot_5.png}\\[-1ex]
  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
  	\end{tabular}
  	\caption{Simulated diffraction patterns generated from trajectories of systems 
  	built in the parallel displaced and sandwiched configurations as a function
  	of water content shows weaker reflections than the dry system.}%
  \label{fig:solvation}

@@

  %BJC: TODO: Bigger fonts
  \begin{figure}
  \centering 
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
        \caption{Parallel Displaced}
        \label{fig:offset_solvated_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
        \caption{Sandwiched}
        \label{fig:layered_solvated_density}
  \end{subfigure}
  \caption{Water fills the membrane pores in the parallel displaced (a) and 
  sandwiched (b) configurations. Sodium ions are distributed fairly uniformly
  within the pore region, defined by a radius of 0.6 nm.}
  \label{fig:water_density}
  \end{figure}
  %MRS4: weird there's a head group peak in the center. Not enough statistics, so shot noise from the r^2 dr weighting?
  %BJC3: Yea, I'm not sure exactly. I'll look more into it. It might one or two head groups that just get stuck there.
  % The pore I picture in the supplemental info is completely cleared of any head groups.

@@

  \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{IC_offset.png}
        \caption{Calculated ionic conductivity using the Nernst-Einstein relation
        and Collective Diffusion model agree with error. Both methods give calculated
        values of ionic conductivity an order of magnitude higher than the experimental
        value.}
        \label{fig:conductivity}
  \end{figure}

@@

  %BJC: add units
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{IC_xlink.png}
	\caption{}~\label{fig:IC_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{dbwl_xlink.png}
	\caption{}~\label{fig:dbwl_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{p2p_xlink.png}
	\caption{}~\label{fig:p2p_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the cross-linked configuration fade
	  relative to the uncross-linked system. The colorbar shown is the same used for
	  the uncross-linked system. (b) The ionic conductivity is smaller relative to the
	  uncross-linked system, but still much larger than the experimental value. When
	  the system is cross-linked, The distance between layers increases (c) and the
	  pore spacing decreases (d)}~\label{fig:xlink}
  \end{figure}

>>>>

  \begin{figure}
  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
  	\rowname{Parallel Displaced}&
  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_25.png}&
  	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]
  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
  	\rowname{Sandwiched}&
  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_25.png}&
  	\includegraphics[width=.325\linewidth]{solvated_layered_rzplot_5.png}\\[-1ex]
  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
  	\end{tabular}
	\caption{Simulated XRD patterns indicate that systems with added water
		are not as structured as the dry systems. As increasing amounts of water are 
		added to both systems, R-$\pi$ fades. When 2.5 wt\% water is added to the
		sandwiched system, R-$\pi$ gains back some intensity, but its magnitude is not
		greater than the dry system. R-spots also disappears as water is added. It is
		absent in all parallel displaced simulations, but fades gradually as water is
		added to the sandwiched configuration.}%
  \label{fig:solvation}

@@

  \begin{figure}
  \centering 
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
        \caption{Parallel Displaced}
        \label{fig:offset_solvated_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
        \caption{Sandwiched}
        \label{fig:layered_solvated_density}
  \end{subfigure}
  \caption{Water fills the membrane pores in the parallel displaced (a) and
	  sandwiched (b) configurations. We define the pore region to be within 0.6 nm of
	  the pore center. Head groups in the sandwiched configuration sit closer to the
	  pore center than they do in the parallel displaced configuration. The parallel
	  displaced pores are composed primarily of water close to the pore center.}
  \label{fig:water_density}
  \end{figure}
  %MRS4: weird there's a head group peak in the center. Not enough statistics, so shot noise from the r^2 dr weighting?
  %BJC3: Yea, I'm not sure exactly. I'll look more into it. It might one or two head groups that just get stuck there.
  % The pore I picture in the supplemental info is completely cleared of any head groups.

@@

  \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{IC_offset.png}
        \caption{The collective diffusion model and the nernst-einstein relation yield
        agreeing values of ionic conductivity. Both methods give calculated
        values of ionic conductivity an order of magnitude higher than the experimental
        value.}
        \label{fig:conductivity}
  \end{figure}

@@

  %BJC: add units
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{IC_xlink.png}
	\caption{}~\label{fig:IC_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{dbwl_xlink.png}
	\caption{}~\label{fig:dbwl_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{p2p_xlink.png}
	\caption{}~\label{fig:p2p_xlink}
  \end{subfigure}
  \caption{Applying our simulated crosslinking mechanism to an equilibrium
	  configuration causes slight changes to the system's physical and structural
	  properties. (a) Reflections produced by the cross-linked configuration are
	  faded relative to the uncross-linked system. (b) The ionic conductivity is
	  smaller relative to the uncross-linked system, but still much larger than the
	  experimental value. When the system is cross-linked, the distance between
	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
  \end{figure}

### 2018-01-09 Ben_Manuscripts/structure_paper/supplemental.tex
More figure/caption updates

  \vspace{1em}
  Monomers were parameterized according to the following procedure:
  \begin{enumerate}
	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch 17.13 with all hydrogen atoms
	drawn out explicitly. We optimized the 3D geometry of the structure using the
	'Clean in 3D' function of MarvinSketch 17.13~\cite{chemaxon_marvinsketch_2017}.
	We saved the structure as a .mol file, then converted it to .pdb format using
	Open Babel 2.4.1 \cite{oboyle_open_2011,noauthor_open_nodate}. 
	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using the .pdb
	structure file as input, we ran \texttt{antechamber}~\cite{wang_automatic_2006}
	using the AM1-BCC charge model. The net charge on the monomer is input as -1
	since the sodium ion will be kept as a separate residue. The output of
	\texttt{antechamber} is used to create Amber topology files with
	\texttt{LEaP}~\cite{case_ambertools16_2016}. A detailed tutorial can be accessed
	elsewhere \cite{walker_antechamber_nodate}.
	\item \textit{Create gromacs topologies from Amber output} : \texttt{LEaP}
	outputs a .inpcrd and a .prmtop file which are Amber topology files. Using
	acpype.py \cite{sousa_da_silva_acpype_2012}, we convert the \texttt{LEaP}
	output into GROMACS .gro and .top files. 
	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the monomer in the box with edges of the
	box at least 3 nm from the monomer on all sides. We ran an energy minimzation
	on the system with the steepest descent algorithm.  Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000K to 50K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory. 
	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
	configuration taken from the annealed trajectory, we reassigned charges using
	\texttt{molcharge} using the am1bccsym method in order to ensure charges 
	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
	The charges in the gromacs topology file (.top) were replaced with the 
	new charges calculated by \texttt{molcharge}. 
	\item \textit{Anneal again to get final structure} : The same simulated
	annealing process was repeated using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from
	the last 10 \% of the trajectory and was used to build all assemblies
	reported (Figure~\ref{fig:monomer}).
  \end{enumerate}

@@

  Any major dependence on initial configuration is addressed in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
  monomers per layer in the sandwiched configuration.

  There are three other parameters whose choice may influence the equilibrium
  structure: initial pore spacing, initial pore radius and initial distance
  between layers. Here we show the results of a sensitivity analysis performed
  on the three parameters. To reduce the size of the sensitivity analysis, we
  only tested systems built with 5 monomers per layer with layers stacked in 
  the parallel displaced configuration. All systems were equilibrated according
  to the dry equilibration procedure.

@@

	  We tested five different initial pore spacings, defined as the
	  distance between the central axis of each pore with all others. To reduce the
	  number of variables, we held the pore radius constant, at 5 \AA~and the
	  distance between layers at 3.7 \AA~since those were the values used in our
	  optimal system in the main text. If the initial pore spacing is chosen to be
	  too small, pore columns abruptly repel each other as soon as they are able to
	  overcome the restraining potential present as part of the dry equilibration
	  procedure. We avoided using systems that exhibit this behavior since the
	  behavior increases the chances of a system to become kinetically trapped in an
	  undesired metastable free energy basin.

@@

	  	\item 39 \AA~: A pore spacing of 39 \AA~is used in order to have a test system
		started with a spacing below the experimental value. As soon as the restraining
		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).

		\item 41 \AA~: A pore spacing of 41 \AA~is chosen since it closely matches the
		experimental pore spacing.  Again, we observe abrupt repulsion of columns once
		the restraining potential is switched to 56 KJ mol$^{-1}$ nm$^{-2}$
		(Figure~\ref{fig:p2p_41}).

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle once the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps are introduced unnecessarily.

@@

		\caption{The pore spacing during the restrained portion of the
			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
			experimental value (a) or at the experimental value (b), there is an abrupt
			change in pore spacing when the position restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA apart (c) the pore spacing
			remains relatively stable. When pores are spaced 50 \AA apart (d), the pore
			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA apart (e), so that monomers
			do not intersect with adjacent pores, and position restraints are reduced to 56
			KJ mol$^{-1}$ nm$^{-2}$, pore spacing changes erratically before stabilizing
			when force constants are reduced to 3 KJ mol$^{-1}$ nm$^{-2}$.} 
		\label{fig:p2p}
	  \end{figure}

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~ and the distance between layers constant at
	  3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each frame is calculated as the
	  average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the timeseries
	  representing the average pore radius at each frame.  Equilibration was detected
	  using \texttt{pymbar.timeseries.detectEquilibration}. The average and standard
	  deviation of pore radii were calculated using only data points collected after
	  equilibration was detected.

@@

          We tested 3 different initial layer spacings, defined as the distance between the planes of 
          aromatic rings in each layer. Systems built with layers stacked 3.7 \AA and 5 \AA apart
	  are discussed extensively in the main text. We will focus the discussion here on systems
	  built with layers stacked 10 \AA apart.

@@

\bibliography{llc.bib}
\end{document}

>>>>

  \vspace{1em}
  We parameterized monomers according to the following procedure:
  \begin{enumerate}
	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch
	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
	explicitly. We optimized the 3D geometry of the structure using the 'Clean in
	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
	converted it to .pdb format using Open Babel 2.4.1
	\cite{oboyle_open_2011,noauthor_open_nodate}. 
	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
	the .pdb structure file as input, we ran
	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
	The net charge on the monomer is input as -1 since the sodium ion we keep it as
	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools_nodate} and the
	output of \texttt{antechamber} to create Amber topology files. A detailed
	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
	\item \textit{Create gromacs topologies from Amber output} : The output
	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
	\texttt{LEaP} output into GROMACS .gro and .top files. 
	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the box with edges of the
	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimzation
	on the system with the steepest descent algorithm. Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000K to 50K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory. 
	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
	configuration taken from the annealed trajectory, we reassigned charges using
	\texttt{molcharge} with the am1bccsym method in order to ensure charges 
	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
	The charges in the GROMACS topology file (.top) were replaced with the 
	new charges calculated by \texttt{molcharge}. 
	\item \textit{Anneal again to get final structure} : We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10 \% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).
  \end{enumerate}

@@

  \vspace{1em}
  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
  monomers per layer in the sandwiched configuration.

  There are three other parameters whose choice may influence the equilibrium
  structure: initial pore spacing, initial pore radius and initial distance
  between layers. Here we show the results of a sensitivity analysis performed
  on the three parameters. To reduce the size of the sensitivity analysis, we
  only tested systems built with 5 monomers per layer with layers stacked in 
  the parallel displaced configuration. We equilibrated all systems according
  to the dry equilibration procedure.

@@

	  We tested five different initial pore spacings, defined as the
	  distance between the central axis of each pore with all others. To reduce the
	  number of variables, we held the pore radius constant, at 6 \AA~and the
	  distance between layers at 3.7 \AA~since those were the values used in our
	  optimal system in the main text. If the initial pore spacing is chosen to be
	  too small, pore columns abruptly repel each other as soon as they are able to
	  overcome the restraining potential present as part of the dry equilibration
	  procedure. We avoided using systems that exhibit this behavior since the
	  behavior increases the chances of a system to become kinetically trapped in an
	  undesired metastable free energy basin.

@@

	  	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to have a test system
		with an intial spacing below the experimental value. As soon as the restraining
		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}).

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily.  The system equilibrates to a pore spacing of 4.27
		$\pm$ 0.06 nm.

@@

		\caption{The pore spacing during the restrained portion of the
			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
			experimental value (a) or at the experimental value (b), there is an abrupt
			change in pore spacing when the position restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
			do not intersect with adjacent pores, and position restraints are reduced to 56
			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
		\label{fig:p2p}
	  \end{figure}

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~ and the distance between layers constant at
	  3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated as the
	  average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the timeseries
	  representing the average pore radius at each frame.  We detected equilibration 
	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
	  and standard deviation of pore radii using only data points collected after
	  equilibration was detected.

@@

	  We tested 3 different initial layer spacings, defined as the distance
	  between the planes of aromatic rings in each layer. Systems built with layers
	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
	  will focus the discussion here on systems built with layers stacked 10~\AA
	  apart.

	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
	  with an initial layer spacing of 10 \AA~immediately after the restrained
	  portion of the equilibration procedure. Since we used position restraints, the
	  simulations were run in the NVT ensemble. When layer spacing is large, such as
	  this situation, there is a significant amount of vacuum space which the monomer
	  attempts to fill. Even if turning pressure control on allows the system to
	  recover the geometry of the hexagonal phase, we would likely need much longer
	  equilibration times, and it will almost certainly get trapped in a metastable
	  configuration that bears no resemblence to the experimental profile.

	  \begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{When layers are initially stacked 10 \AA~apart and the system
                is equilibrated using the dry equlibration procedure, large vacuum gaps
		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
	  \end{figure}

@@

\clearpage
\bibliography{llc.bib}
\end{document}
